Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-16 paper_I/ms.tex
add another list of labelled variable stars

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO
% * update keywords per new AAS format

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) is providing
  precise time-series photometry for almost every star cluster in the
  solar neighborhood.
  % Aims
  Using the TESS images, we have begun a Cluster Difference Imaging
  Photometric Survey (CDIPS), in which we are focusing on stars that
  are candidate cluster members, or else show other indications of
  youth.
  %
  Our aims are to discover giant transiting planets with known ages,
  and to provide light curves suitable for studies in stellar
  astrophysics.
  %
  For this work, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.  Each light curve
  represents between 20 and 25 days of observations of a star brighter
  than $G_{Rp}=16$, with 30-minute sampling.
  % Methods
  We describe the image subtraction and time-series analysis
  techniques we used to create the light curves, which have noise
  properties that agree with theoretical expectations.
  %
  We also comment on the possible utility of the light curve sample
  for studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves, which cover about one sixth of the galactic plane,
  are available at \stscilink.
\end{abstract}

@@

A major barrier to deriving precise photometry from the TESS images is
the relatively poor angular resolution ($21''$ per pixel).   The
problems with crowding and complex backgrounds are so severe that the
TESS Candidate Target List deprioritizes 2-minute targets within
$15^\circ$ of the galactic plane\footnote{During the first year of
TESS observations, objects within $15^\circ$ of the galactic plane
were deprioritized. Starting in the second year of observations, the
cutoff changed to objects within $10^\circ$ of the galactic plane
\citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
This decision was made because the large pixel size and the high
stellar surface density make aperture photometry unreliable.  However,
it implies that most stars in clusters, which are almost always near
the galactic plane, will go unprocessed by the official {\it TESS}
data reduction pipeline.

@@

We have therefore begun to apply difference imaging to the TESS
FFIs, with a focus on any star that could be a member of a group.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  A major motivation
for this effort is to discover giant transiting planets with known
ages.  The focus of the present study however is to describe our
methods, and to produce a general-purpose dataset applicable for
studies both in exoplanetary and also stellar astrophysics.

@@

The plan of action is as follows. In \S~\ref{sec:starselection}, we
describe how target stars were selected. We then present the
photometric and image processing methods we used to produce light
curves for these stars (\S~\ref{sec:method}).  In TESS Sectors 6 and
7, these methods yielded \numberlcs light curves, and in
\S~\ref{subsec:lcstatistics} we summarize their statistical
properties.  An example of how we might use the data to identify
pulsating stars, eclipsing binaries, and transiting planets is then
given (\S~\ref{subsec:identifying_variability}).  We close in
\S~\ref{sec:conclusion} by summarizing our findings, and discuss them
with an eye towards the studies we hope this and further data
processing will enable.

@@

First, we describe the catalogs we used to identify members of open
clusters (\S~\ref{subsec:oc}).  Then, we discuss the catalogs we used
to identify members of moving groups, stellar associations, and more
generally young stellar populations (\S~\ref{subsec:mg}).  In
\S~\ref{subsec:ocmgsummary} and Figure~\ref{fig:cdips_targets} we give
summary statistics for the entire sample of about one million target
stars.

@@

At the time of writing, two relatively large, homogeneous cluster
memberships studies had been performed using Gaia-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.  There were
also two large membership studies pre-dating Gaia-DR2 based on proper
motion and photometric catalogs: the studies of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.

@@

\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
assignment algorithm \citep{krone-martins_upmask_2014} to identify
cluster members using Gaia-DR2 positions, proper motions, and
parallaxes.  They used Gaia photometry and radial velocities to verify
the membership claims.  From their Table~2, we collect 401{,}448
cluster members, in 1229 clusters, down to their limiting magnitude of
$G=18$.

\citet{gaia_hr_2018} reported members of a smaller, more select group
of well-studied open clusters. From their Table~A1, we collect
40{,}903 cluster members, in 41 open clusters, mostly within
$500\,{\rm pc}$. While this work also included memberships for
globular clusters, we omitted them from consideration.

@@

\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations (globular clusters were omitted by
excluding any entry of type \texttt{'g'}).  We selected the most
probable cluster members (``$1\sigma$ members'') using the combined
photometric, kinematic, and spatial criteria described by
\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
Gaia}-DR2 source identifiers for the members, we performed a
crossmatch for Gaia-DR2 sources within 5 arcseconds of the listed
positions.  To improve the quality of the cross-match, we used the
2MASS photometry to predict the $G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
(accessed \texttt{2019-03-29}), or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

The second (non-{\it Gaia} derived) open cluster membership catalog we
used was the \citet{dias_proper_2014} catalog, which was based on
UCAC4 proper motions acquired by the US Naval Observatory
\citep{zacharias_fourth_2013}.  From their 1805 reported open
clusters, we selected sources with quoted membership probability above
50\%.  To obtain Gaia-DR2 source identifiers for the members, we
performed a similar crossmatch as before, looking for sources within 5
arcseconds of the listed positions, and within $\pm$2 $G$-band
magnitudes of the prediction.  From 2{,}034{,}269 stars, this yielded
a unique best neighbor for 1{,}828{,}630 stars (89.9\% of the sample),
and a choice between two neighbors for 8.7\% of the remaining sample.

The distributions of various cross-matching statistics are shown in
Figure~\ref{fig:xmatch_info}.  The distances between matches is
typically below 1 arcsecond.  The \citeauthor{dias_proper_2014}
catalog shows stronger crowding effects at the faint end compared to
the \citeauthor{Kharchenko_et_al_2013} catalog, and likely has a
larger number of false matches.  At their faint ends, both catalogs
show a tendency for true $G$-band magnitudes to be larger than
predicted $G$-band magnitudes, presumably due to dust reddening.

@@

Stars, moving groups and stellar associations are of interest for
similar reasons as stars in open clusters.  Though fewer stars
are known to exist in moving groups, they are of particular interest
because moving groups are less crowded than open clusters, and are
often closer to the Sun.

We obtained Gaia-DR2 identifiers from the results of the following
studies:
\citet{gagne_banyan_XI_2018},
\citet{gagne_banyan_XII_2018},
\citet{gagne_banyan_XIII_2018},
\citet{kraus_tucanahor_2014},
\citet{roser_deep_2011}, % OC, not MG...
\citet{bell_32ori_2017},
\citet{rizzuto_multidimensional_2011},
\citet{oh_comoving_2017}, and
\citet{zari_3d_2018}. The methods applied in these studies
vary from kinematic analyses, to astrometric analyses included
Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
spectroscopic studies including RVs, H$\alpha$
emission, and Li absorption.

@@

\citet{oh_comoving_2017} searched for comoving stars in the $\approx$2
million stars that appear in both the Tycho-2 and {\it Gaia}-DR1
catalogs.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
Gaia-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

Finally, \citet{zari_3d_2018} constructed a sample of young stars
within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
careful combination of distinct astrometric and photometric cuts.
These stars are the youngest, closest stars, spread across
star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
regions of the sky.  Though most of these stars are not directly
identified with moving groups or open clusters, their reported youth
and proximity to star forming regions justifies their inclusion in our
search sample.

@@

After collecting the aforementioned lists, we merged them into a
single table. We queried Gaia-DR2's \texttt{gaia\_source} table to
retrieve their apparent $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
magnitudes, as well as their astrometric measurements $(\alpha,
\delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
$G_{\rm Rp} < 16$, which is roughly the level for which the 1-hour
photometric precision of TESS is predicted to be 1\%
\citep{ricker_transiting_2015}.

@@

Different catalogs have different standards for deciding which stars
are members.  For the \citet{dias_proper_2014} catalog, their
membership calculation included only spatial and kinematic
information, and we used a relatively low probability threshold when
including their stars (based on the criteria
\citealt{dias_proper_2014} used for their star counts).  The
\citet{Kharchenko_et_al_2013} catalog combined spatial, kinematic, and
photometric information to derive their membership probabilities.  We
also used a more restrictive membership probability cut (again,
following the criteria they used for their star counts), and so this
sub-sample is likely less contaminated with field interlopers.
\citet{cantat-gaudin_gaia_2018} used spatial, kinematic, and
astrometric information from Gaia-DR2. Despite the lack of photometric
information, the quality of the Gaia data suggest that the field
contamination rate will be lowest for the
\citet{cantat-gaudin_gaia_2018} sample.

To assign unique cluster names, we adopted the name given by
\citet{Kharchenko_et_al_2013} whenever possible.
Appendix~\ref{appendix:uniquenames} describes  how this was done in
detail.  For moving groups not identified by
\citet{Kharchenko_et_al_2013}, we used the constellation-based naming
convention from \citet{gagne_banyan_XI_2018}.  Otherwise, we used the
name reported by the original catalog claiming membership.  This
process reduced 16,425 name variants down to 3,216 unique cluster
names.  Though we have made every effort to avoid duplicates, a small
number may remain, so we advise inspection of the \texttt{cluster}
column as well as the references given in the \texttt{reference}
column rather than using the \texttt{unique\_cluster\_name} column to
analyze individual objects of interest.  Nonetheless, 87.7\% of the
$\sim$million unique target stars are matched to clusters named by
\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
The remainder are mostly the young stars from \citet{zari_3d_2018}.
Ages and their uncertainties were then assigned using the parameters
reported by \citet{Kharchenko_et_al_2013}.

@@

To reduce the TESS images to light curves, we adopted a difference
imaging approach.  The overall method is in the spirit of the
pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017},
\citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
Figure~\ref{fig:pipeline} shows a conceptual overview of our pipeline.
Most modules have been developed over the past decade to reduce images
taken by the Hungarian Automated Telescope (HAT) network
\citep{bakos_hat_review_2018}.  The work of \citet{Pal_2009}, embodied
in the \texttt{fitsh} software package, was an especially crucial
component.  The specific high-level framework we used for this
reduction was adapted from a pipeline called \texttt{pipe-trex}, under
development primarily for the HATPI project (\url{hatpi.org}).  The
code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{9d7020e}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images.  To
construct a photometric reference frame, we first convolve a subset of
the frames to have identical stellar profiles, and then stack them.
Finally, we subtract each target frame from the photometric reference
frame (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from the Gaia-DR2 source catalog.  The resulting differential
flux measurements are converted to total flux measurements using
photometric information from Gaia-DR2 to estimate the total flux of
each source on the reference image.  We detrend the resulting light
curves (\S~\ref{subsec:lcdetrending}).  The resulting white noise and
red noise properties of the light curves, and a few interesting cases
of variability, are discussed in \S~\ref{sec:results}.

@@

Sectors 1--5 mainly covered portions of the sky away from the galactic
plane.  Consequently, fewer than 2\% of the CDIPS target stars were
observed in the first five TESS sectors.  Although a few interesting
clusters are present in these observations ({\it e.g.}, Blanco~1,
NGC~2516, NGC~1901), for the present work we opted to focus on Sectors
6 \& 7, for which there were more stars of interest.  These begin in
Sector 6 (2018-12-12, spacecraft orbit \#19), and conclude at the end
of Sector 7 (2019-02-01, spacecraft orbit \#22).  Sectors 6 and 7
cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$,
with coverage within $\pm 20^\circ$ of the galactic plane
(Figure~\ref{fig:cdips_targets_positions}).

@@

Having prepared the images, we perform some initial analysis steps to
produce metadata needed during image subtraction.

First, we perform source extraction on the thousand or so brightest,
non-saturated stars in each image.  This is done using a
\texttt{fitsh} tool, \texttt{fistar}.  We derive centroid positions
for the stars, and simultaneously fit elliptical gaussians to their
profiles, yielding the shape parameters $(s,d,k)$, where the flux $f$
as a function of position $(x,y)$ in the CCD image plane is assumed to
take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star, $\Delta x =
x-x_0$, $\Delta y = y - y_0$, $B$ the background level, and $A$ an
arbitrary flux-scaling constant.  For a nearly circular shape profile,
the sharpness $s$ is related to the FWHM as ${\rm FWHM} \approx
2.35s^{-1/2}$ \citep[{\it e.g.},][]{Pal_2009}.  These shape parameters
are later used when selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  In agreement with what is obvious
upon visual inspection, this fitting process shows that stars closer
to the center of each camera's field are round, while stars near the
field edges are more elongated.

@@

The core operation of ``classical'' image subtraction is to match a
photometric reference image $R$ and a target image $I$ by computing
and applying a convolution kernel.  For ground-based data, this
``match'' typically corrects for differences in seeing or transparency
between the reference and target; for space-based data, the match
might correct for spacecraft jitter, or thermal and corresponding
point-spread function (PSF) variations.  The kernel, once applied to
the high signal-to noise reference, produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
    \label{eq:imagemodel}
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations, and $\otimes$ denotes convolution.  Since we
modeled the background separately (\S~\ref{subsec:preparation}), we
set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
onto a basis,
\begin{equation}
K = \sum_i c_i K_i,
\end{equation}
where the coefficients $c_i$ are found by minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
where $\sigma_{xy}$ is the uncertainty in the target image pixel
values.  Photometry is then performed on the difference image
$D_{xy}$, where $D_{xy} = I_{xy} - M_{xy}$.  For the present
reduction, the uncertainty in each target image pixel was taken to be
a constant.

@@

To choose the astrometric reference frame, we search for frames with
compact, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have a low background level, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference frame
needs to have a large number of detected sources (though the variance
between TESS images was rather small).  We sort the image using these
metrics, and then select the astrometric reference frame from
successive intersections of each sorted list.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) is providing
  precise time-series photometry for most star clusters in the
  solar neighborhood.
  % Aims
  Using the TESS images, we have begun a Cluster Difference Imaging
  Photometric Survey (CDIPS), in which we are focusing 
  both on stars that are candidate cluster members, and on stars that show indications of youth.
  %
  Our aims are to discover giant transiting planets with known ages,
  and to provide light curves suitable for studies in stellar
  astrophysics.
  %
  For this work, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.  Each light curve
  represents between 20 and 25 days of observations of a star brighter
  than $G_{Rp}=16$, with 30-minute sampling.
  % Methods
  We describe the image subtraction and time-series analysis
  techniques we used to create the light curves, which have noise
  properties that agree with theoretical expectations.
  %
  We also comment on the possible utility of the light curve sample
  for studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves, which cover about one sixth of the galactic plane,
  are available at \stscilink.
\end{abstract}

@@

A major barrier to deriving precise photometry from the TESS images is
the relatively poor angular resolution ($21''$ per pixel).   The
problems with crowding and complex backgrounds are so severe that the
TESS Candidate Target List deprioritizes 2-minute targets within
$15^\circ$ of the galactic plane\footnote{During the first year of
TESS observations, objects within $15^\circ$ of the galactic plane
were deprioritized. Starting in the second year of observations, the
cutoff changed to objects within $10^\circ$ of the galactic plane
\citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
This decision was made because the large pixel size and the high
stellar surface density make aperture photometry unreliable.  However,
it implies that most stars in clusters, which are usually near
the galactic plane, will go unprocessed by the official {\it TESS}
data reduction pipeline.

@@

We have therefore begun to apply difference imaging to the TESS
FFIs, with a focus on any star that could be a cluster member.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  A major motivation
for this effort is to discover giant transiting planets with known
ages.  The focus of the present study however is to describe our
methods, and to produce a general-purpose dataset applicable for
studies both in exoplanetary and also stellar astrophysics.

@@

The plan of action is as follows. In \S~\ref{sec:starselection}, we
describe how target stars were selected. We then present the
photometric and image processing methods we used to produce light
curves for these stars (\S~\ref{sec:method}).  In TESS Sectors 6 and
7, these methods yielded \numberlcs light curves, and in
\S~\ref{subsec:lcstatistics} we summarize their statistical
properties.  We then give an example of how to use the data to identify
pulsating stars, eclipsing binaries, and transiting planets
(\S~\ref{subsec:identifying_variability}).  We close in
\S~\ref{sec:conclusion} with a summary of our findings, and discuss them
with an eye towards the studies we hope this and further data
processing will enable.

@@

First, we describe the catalogs we used to identify members of open
clusters (\S~\ref{subsec:oc}).  Then, we discuss the catalogs we used
to identify members of moving groups, stellar associations, and more
generally young stellar populations (\S~\ref{subsec:mg}).  In
\S~\ref{subsec:ocmgsummary} we give
summary statistics for the entire sample of about one million target
stars, and we list the targets in Table~\ref{tbl:cdips_targets}.

@@

At the time of our analysis, two relatively large, homogeneous cluster
memberships studies had been performed using Gaia-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.  There were
also two large membership studies pre-dating Gaia-DR2 based on proper
motion and photometric catalogs: the studies of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.

@@

\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
assignment algorithm \citep{krone-martins_upmask_2014} to identify
cluster members using Gaia-DR2 positions, proper motions, and
parallaxes.  They used Gaia photometry and radial velocities to verify
the membership claims.  From their Table~2, we collected 401{,}448
cluster members, in 1229 clusters, down to their limiting magnitude of
$G=18$.

\citet{gaia_hr_2018} reported members of a smaller, more select group
of well-studied open clusters. From their Table~A1, we collected
40{,}903 cluster members, in 41 open clusters, mostly within
$500\,{\rm pc}$. While this work also included memberships for
globular clusters, we omitted them from consideration.

@@

\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations. We omitted globular clusters by
excluding any entry of type `\texttt{g}'.  We selected the most
probable cluster members (``$1\sigma$ members'') using the combined
photometric, kinematic, and spatial criteria described by
\citet{kharchenko_global_2012}.  Then, to obtain {\it
Gaia}-DR2 source identifiers for the members, we performed a
crossmatch for Gaia-DR2 sources within 5 arcseconds of the listed
positions.  To improve the quality of the cross-match, we used the
2MASS photometry to predict the $G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
(accessed \texttt{2019-03-29}), or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

The second (non-{\it Gaia} derived) open cluster membership catalog we
used was the \citet{dias_proper_2014} catalog, which was based on
UCAC4 proper motions acquired by the US Naval Observatory
\citep{zacharias_fourth_2013}.  From their 1805 reported open
clusters, we selected sources with quoted membership probability above
50\%.  To obtain Gaia-DR2 source identifiers for the members, we
performed a similar crossmatch, looking for sources within 5
arcseconds of the listed positions, and within $\pm$2 $G$-band
magnitudes of the prediction.  From 2{,}034{,}269 stars, this yielded
a unique best neighbor for 1{,}828{,}630 stars (89.9\% of the sample),
and a choice between two neighbors for 8.7\% of the remaining sample.

The distributions of various cross-matching statistics are shown in
Figure~\ref{fig:xmatch_info}.  The distances between matches is
typically below 1 arcsecond.  The \citeauthor{dias_proper_2014}
catalog shows stronger crowding effects at the faint end than
the \citeauthor{Kharchenko_et_al_2013} catalog, and likely has a
larger number of false matches.  At their faint ends, both catalogs
show a tendency for true $G$-band magnitudes to be larger than
predicted $G$-band magnitudes, presumably due to dust reddening.

@@

Stars in moving groups and stellar associations are interesting for
similar reasons as stars in open clusters.  
Relative to open cluster members though, stars in moving groups are 
usually closer, brighter, and
exist in less crowded environments.

To identify stars in these types of groups, we matched the following studies
against Gaia-DR2:
\citet{gagne_banyan_XII_2018},
\citet{gagne_banyan_XI_2018},
\citet{gagne_banyan_XIII_2018},
\citet{kraus_tucanahor_2014},
\citet{roser_deep_2011}, % OC, not MG...
\citet{bell_32ori_2017},
\citet{rizzuto_multidimensional_2011},
\citet{oh_comoving_2017}, and
\citet{zari_3d_2018}. The methods applied in these studies
vary from kinematic analyses, to astrometric analyses included
Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
spectroscopic studies including RVs, H$\alpha$
emission, and Li absorption.

@@

\citet{oh_comoving_2017} searched for comoving stars in the $\approx$2
million stars that appear in both the Tycho-2 and Gaia-DR1
catalogs.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
Gaia-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

Finally, \citet{zari_3d_2018} constructed a sample of young stars
within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
made: an upper main sequence (MS) sample, with 86{,}102 stars, and
a pre-MS sample, with 43{,}719 stars.  Each was created from a
careful combination of distinct astrometric and photometric cuts.
These stars are the youngest, closest stars, spread across
star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
regions of the sky.  Though most of these stars are not directly
identified with moving groups or open clusters, their reported youth
and proximity to star forming regions justifies their inclusion in our
search sample.

@@

After collecting the aforementioned lists, we merged them into a
single table. We queried Gaia-DR2's \texttt{gaia\_source} table to
retrieve each star's apparent $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
magnitudes, as well as their astrometric measurements $(\alpha,
\delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
$G_{\rm Rp} < 16$, which is roughly the level for which the 1-hour
photometric precision of TESS is predicted to be 1\%
\citep{ricker_transiting_2015}.

@@

Different catalogs have different standards for deciding which stars
are members.  For the \citet{dias_proper_2014} catalog, their
membership calculation included only spatial and kinematic
information, and we used a relatively low probability threshold when
including their stars (based on the criteria
\citealt{dias_proper_2014} used for their star counts).  The
\citet{Kharchenko_et_al_2013} catalog combined spatial, kinematic, and
photometric information to derive their membership probabilities.  We
also used a more restrictive membership probability cut (again,
following the criteria they used for their star counts), so this
sub-sample is likely less contaminated with field interlopers.
\citet{cantat-gaudin_gaia_2018} used spatial, kinematic, and
astrometric information from Gaia-DR2. Despite the lack of photometric
information, the quality of the Gaia data suggest that the field
contamination rate will be lowest for the
\citet{cantat-gaudin_gaia_2018} sample.

To assign unique cluster names, we adopted the name given by
\citet{Kharchenko_et_al_2013} whenever possible.
Appendix~\ref{appendix:uniquenames} describes  how this was done in
detail.  For moving groups not identified by
\citet{Kharchenko_et_al_2013}, we used the constellation-based naming
convention from \citet{gagne_banyan_XI_2018}.  Otherwise, we used the
name reported by the original catalog claiming membership.  This
process reduced 16,425 name variants down to 3,216 unique cluster
names.  Though we have made every effort to avoid duplicates, a small
number may remain, so we advise inspection of the \texttt{cluster}
column as well as the references given in the \texttt{reference}
column rather than using the \texttt{unique\_cluster\_name} column to
analyze individual objects of interest.  Nonetheless, 87.7\% of the
$\sim$million unique target stars are matched to clusters named by
\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
The remainder are mostly young stars from \citet{zari_3d_2018}.
Ages and their uncertainties were then assigned using the parameters
reported by \citet{Kharchenko_et_al_2013}.

@@

To reduce the TESS images to light curves, we adopted a difference
imaging approach.  The overall method is in the spirit of the
pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017},
\citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
Figure~\ref{fig:pipeline} shows a conceptual overview of our pipeline.
Most modules have been developed over the past decade to reduce images
taken by the Hungarian Automated Telescope (HAT) network
\citep{bakos_hat_review_2018}.  The work of \citet{Pal_2009}, embodied
in the \texttt{fitsh} software package, was an especially crucial
component.  The specific high-level framework we used for this
reduction was adapted from a pipeline called \texttt{pipe-trex}, under
development for the HATPI project (\url{hatpi.org}).  The
code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{9d7020e}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images.  To
construct a photometric reference frame, we first convolve a subset of
the frames to have identical stellar profiles, and then stack them.
Finally, we subtract each target frame from the photometric reference
frame (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from the Gaia-DR2 source catalog.  The resulting differential
flux measurements are converted to total flux measurements using
photometric information from Gaia-DR2 to determine the total flux of
each source on the reference image.  We detrend the resulting light
curves (\S~\ref{subsec:lcdetrending}).  The resulting white noise and
red noise properties of the light curves, and a few interesting cases
of variability, are explored in \S~\ref{sec:results}.

@@

Sectors 1--5 mainly covered portions of the sky away from the galactic
plane.  Consequently, fewer than 2\% of the CDIPS target stars were
observed in the first five TESS sectors.  Although a few interesting
clusters are present in these observations ({\it e.g.}, Blanco~1,
NGC~2516, NGC~1901), for the present work we opted to focus on Sectors
6 and 7, for which there were more stars of interest.  Sector 6
began on December 12, 2018 (space orbit \#19). Sector 7 concluded
on February 1, 2019. Combined, the two sectors
cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$,
with coverage within $\pm 20^\circ$ of the galactic plane
(Figure~\ref{fig:cdips_targets_positions}).

@@

After preparing the images, we perform some initial analysis steps to
produce metadata needed during image subtraction.

First, we perform source extraction on the thousand or so brightest,
non-saturated stars in each image.  This is done using a
\texttt{fitsh} module, \texttt{fistar}.  We derive centroid positions
for the stars, and simultaneously fit elliptical gaussians to their
profiles, yielding the shape parameters $(s,d,k)$, where the flux $f$
as a function of position $(x,y)$ in the CCD image plane is assumed to
take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star, $\Delta x =
x-x_0$, $\Delta y = y - y_0$, $B$ the background level, and $A$ an
arbitrary flux-scaling constant.  For a nearly circular shape profile,
the sharpness $s$ is related to the FWHM as ${\rm FWHM} \approx
2.35s^{-1/2}$ \citep[{\it e.g.},][]{Pal_2009}.  These shape parameters
are later used when selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  In agreement with what is obvious
upon visual inspection, this fitting process shows that stars closer
to the center of each camera's field are round, while stars near the
field edges are more elongated.

@@

The core operation of ``classical'' image subtraction is to match a
photometric reference image $R$ and a target image $I$ by computing
and applying a convolution kernel.  For ground-based data, this
``match'' typically corrects for differences in seeing or transparency
between the reference and target; for space-based data, the match
might correct for spacecraft jitter, or thermal and corresponding
point-spread function (PSF) variations.  The kernel, once applied to
the high signal-to noise reference, produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
    \label{eq:imagemodel}
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations, and $\otimes$ denotes convolution.  Since we
modeled the background separately (\S~\ref{subsec:preparation}), we
set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
onto a basis,
\begin{equation}
K = \sum_i c_i K_i,
\end{equation}
where the coefficients $c_i$ are found by minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
for $\sigma_{xy}$ the uncertainty in the target image pixel
values.  Photometry is then performed on the difference image
$D_{xy}$, where $D_{xy} = I_{xy} - M_{xy}$.  For the present
reduction, the uncertainty in each target image pixel was taken to be
a constant.

@@

To choose the astrometric reference frame, we search for frames with
compact, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have a low background level, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference frame
needs to have a large number of detected sources (though the variance
between TESS images was rather small).  We sort the images using these
metrics, and then select the astrometric reference frame from
successive intersections of each sorted list.
